---
title: "Simulation"
output: 
  html_document:
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set a seed value
set.seed(123)
```

# 1. Samples
Sample 100 samples from a standard normal distribution.
Example study: a school with a 1000 students, IQ is measured (mean 100, sd = 15).
This study is replicated a 100 times. 

```{r}
n <- 1000
mu <- 100
s <- 15
samples <- replicate(100, rnorm(n, mean = mu, sd = s))
```


# 2. Statistics 
For each of these samples, calculate the following statistics for the mean

Absolute bias:

$$|\bar{x} - \mu| $$
  
  
  
Standard error of the mean: 

$$\sigma_\bar{x}  = \frac{\sigma}{\sqrt{n}}$$



Where $\sigma = \sqrt{\frac{1}{n} \Sigma(x_i - \mu)^2}$



Lower and upper bound of the 95% confidence interval: 

$$ \bar{x} \pm 1.96 \frac{\sigma}{\sqrt{n}} $$




```{r}
# retry
info <- function(x){
  m <- mean(x)
  sem <- sd(x)/sqrt(n)
  output <- c(
    m,
    abs(m - mu),
    sem,
    m - 1.96*sem,
    m + 1.96*sem)
    
    return(output)
}

results2 <- t(apply(samples, 2, info))
colnames(results2) <- c("Mean", "bias", "sem", "lb", "ub")
results2 <- data.frame(results2)

# add variable on type1 errors
library(magrittr)
results2 <- results2 %>%
            dplyr::mutate(typeone = mu > lb & mu < ub)
```

# 3. Plot
Create a plot that demonstrates the following

>"A replication of the procedure that generates a 95% confidence interval that is centered around the sample mean would cover the population value at 
    least 95 out of 100 times" [(Neyman, 1934)](https://www.google.nl/url?sa=t&rct=j&q=&esrc=s&source=web&cd=1&ved=0ahUKEwjk4LaD6LrXAhUGC8AKHdATBhMQFggoMAA&url=http%3A%2F%2Fwww.stat.cmu.edu%2F~brian%2F905-2008%2Fpapers%2Fneyman-1934-jrss.pdf&usg=AOvVaw3KRw9DSklPihrYIM0_zRrC)
    
```{r}
library(ggplot2)
ggplot(data = results2, aes(x = 1:100, y = Mean, color = typeone)) + 
  geom_pointrange(aes(ymin = lb, ymax = ub)) +
  xlab("Sample mean + 95% CI") +
  ylab("Samples 1:100") +
  theme_minimal()
```

# 4. Table
Present a table containing all simulated samples for which the resulting confidence interval does 
not contain the population value.

```{r}
library(knitr)
library(kableExtra)
kable(results2[!results2$typeone, -6], caption = "Samles containing a Type 1 error") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
```

